Test-driven Knowledge Graph Construction

### 2023-05-08 doc/paper4.tex
Move ontology terms to the correct step

\section{Limitations}
We are aware of several limitations of the proposed method. Here we recount some of them and suggest how to remedy them. The method may cause the developed artifacts outlined in the Figure \ref{fig:process} to overfit the user requirements in scope, which would hinder the reuse of the artifacts. This shortcoming can be remedied by including more CQs or focusing on reusability during refactoring. User requirements for the knowledge graph under construction can be more complex than what SPARQL can express. One way around it is formalizing the requirements in a more expressive programming language that extends SHACL, such as in \cite{SHACLJS2017}. Ultimately, in order to ameliorate the limitations of this method, it is best combined with other methods, such as those for ontology design (e.g., Kendall and McGuinness \cite{Kendall2019}). Discovering additional limitations of the method in its future applications in constructing knowledge graph in various settings may help inform and progressively refine the method.

@@

\textbf{Step 2:} We continued with analysis of the CQs and extraction of terms and relations, such as \textit{"sensitivity"}, \textit{"test"}, or \textit{"has manufacturer"} from the given example question; see Listing \ref{lst:example-onto}. Since we did not have many CQs, we extracted the terms and relations manually.

@@

\textbf{Step 3:} The third step was to create a minimum viable ontology from the extracted terms and relations, which we did mostly by reusing existing ontology terms and using RDF Schema. For what we did not find suitable terms to reuse, we formalised terms in the simple Antigen Covid Test Ontology. This ontology aimed to allow expressing the CQs in SPARQL.

>>>>

\section{Limitations}
We are aware of several limitations of the proposed method. Here we recount some of them and suggest how to remedy them. The method may cause the developed artifacts outlined in the Figure \ref{fig:process} to overfit the user requirements in scope, which would hinder the reuse of the artifacts. This shortcoming can be remedied by including more CQs or focusing on reusability during refactoring. User requirements for the knowledge graph under construction can be more complex than what SPARQL can express. One way around it is formalizing the requirements in a more expressive programming language that extends SHACL, such as in \cite{SHACLJS2017}. Ultimately, in order to ameliorate the limitations of this method, it is best combined with other methods, such as those for ontology design (e.g., Kendall and McGuinness \cite{Kendall2019}).

@@

\textbf{Step 2:} We continued with analysis of the CQs and extraction of terms and relations, such as \textit{"sensitivity"}, \textit{"test"}, or \textit{"has manufacturer"} from the given example question. Since we did not have many CQs, we extracted the terms and relations manually.

\textbf{Step 3:} The third step was to create a minimum viable ontology from the extracted terms and relations, which we did mostly by reusing existing ontology terms and using RDF Schema; see Listing \ref{lst:example-onto}. For what we did not find suitable terms to reuse, we formalised terms in the simple Antigen Covid Test Ontology. This ontology aimed to allow expressing the CQs in SPARQL.

@@
